High-accuracy neutron diffusion calculations based on integral transport theory

### 2019-12-12 docs/EPJP2019/Gross-EPJP-2019.tex
Updated figures of convergence
Modified plots
Changed caption
Fixed caption from 200 iterations -> 1000 iterations

\begin{figure}[htbp]
	% convergence
	\centering
	\includegraphics[width=0.65\linewidth]{epsilon.pdf}	
	%\includegraphics[width=0.4\linewidth]{convergence.pdf}
	\caption{Convergence of the flux (max deviation) and of the criticality
		eigenvalue during 200 Ronen iterations.}
	\label{fig:conv}
\end{figure}

@@

% convergence
\begin{figure}[hbtp]
	\centering
	\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_1_sn.pdf}
	\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_2_sn.pdf}
	\caption{The spatial flux convergence of the Ronen iterations with respect to the reference $S_{16}$ solution for the left half slab.}
	\label{fig:conv3}
\end{figure}

>>>>

\begin{figure}[htbp]
	% convergence
	\centering
	\includegraphics[width=0.65\linewidth]{epsilon1000.pdf}	
	%\includegraphics[width=0.4\linewidth]{convergence.pdf}
	\caption{Convergence of the flux (max deviation) and of the criticality
		eigenvalue during 1000 Ronen iterations.}
	\label{fig:conv}
\end{figure}

@@

% convergence
\begin{figure}[hbtp]
	\centering
	\includegraphics[width=0.65\linewidth]{RM_Sn_converg_FAST.pdf}
	\includegraphics[width=0.65\linewidth]{RM_Sn_converg_THERMAL.pdf}
	\caption{The spatial flux convergence of the Ronen iterations with respect to the reference $S_{16}$ solution for the left half slab.}
	\label{fig:conv3}
\end{figure}
